---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
 

Database Multpile Queries

--- Attempt 1 - join statements with a ';' and let sql sort it on db side. (Example doesn't run)

```{r}
dbSendQuery(chp,paste(paste(nondup_qry[nondup_df[,'is_checked']==1],collapse=';'),';',sep = ''))
```

--- Attempt 2 - Try to create table and append values e.g.

```{r}
query <- "insert into table (col1,col2,...)
       values 
        (val1,val2,...)
        on conflict (primary_Key) do update set
        (col1,col2,...)
        col1 = EXCLUDED.col1,col2 = EXCLUDED.col2,..."
```

as a function with a dataframe input...

```{r}
#takes name of parent table to update, data, col in parent table to match (pk1) to pk2 in data
update_or_insert <- function(table_name,data,pk){
  #change dataframe to csv string
  rows <- apply(data,1,function(row) return(paste(row,collapse=',')))
  string <- paste("(",paste(rows,collapse='),('),")",sep = "")
  
  #generate sql query
  columns_match <- paste(lapply(colnames(data),function(col) return(sprintf("%s = EXCLUDED.%s",col,col))),collapse=',')
  columns <- paste(colnames(data),collapse=',')
  full_string <- sprintf("insert into %s (%s)
                       values %s
                       on conflict (%s) do update set %s",table_name,columns,string,pk,columns_match)
  
  gsub('NA','Null::int',full_string)
}
```

** Failure due to id being assigned as a sequence by the db. Hence ID is not included when inserting and id would not be a column in the dataframe so conflict would never be called.

Working Attempt: Use with-as statements for the query

```{r}
create_update_v3 <- function(table_name,data,pk){
  
  #check primary key exists in data if not make null
  if ( !(pk %in% colnames(data)) ){
    data[pk] = rep("NA",nrow(data))
  }
  
  #change dataframe to csv string
  rows <- apply(data,1,function(row) return(paste(row,collapse=',')))
  string <- paste("(",paste(rows,collapse='),('),")",sep = "")
  
  #generate sql query
  columns_match <- paste(lapply(colnames(data),function(col) return(sprintf("%s = u.%s",col,col))),collapse=',')
  columns <- paste(colnames(data),collapse=',')
  columns_no_pk <- colnames(data)[colnames(data) != pk] %>% paste(collapse=',')
  
  full_string <- sprintf("with
                          all_ids as (
                            select * from 
                            (
                              values %s
                            )
                            as t (%s)
                          ),
                          update_ids as (select * from all_ids where %s is not NULL),
                          insert_ids as (select * from all_ids where %s is NULL),
                          update_qry as (UPDATE %s t set %s from update_ids u where t.%s=u.%s)
                          insert into %s (%s) select %s from insert_ids;                       
                           ",string,columns,pk,pk,table_name,columns_match,pk,pk,table_name,columns_no_pk,columns_no_pk)
  gsub('NA','Null::int',full_string)
}
```

